\section{The remaining gaps, exhaustively}\label{sec:remaining}

This section is the paper's ledger: Theorem~\ref{thm:conditional}
(rung ii) is claimed modulo exactly the items below. \textbf{After the
adversarial verification pass (June 10, late), the honest summary is:}
the \emph{unweighted digit layer} is solid (proved modulo the open but
benign-diagnosed E1--E2); the \emph{weighted/anatomy layers} rest on
two genuinely structural open hypotheses, E3
(Hypothesis~\ref{hyp:E3}) and C$^\dagger$
(Hypothesis~\ref{hyp:Cdagger}) --- both beyond-$\sqrt{}$ dispersion
statements, both empirically true with square-root room, both
parity-free. The remaining items below are citation debts and
mechanical write-ups.

\subsection*{Structural open hypotheses (final state, June 11)}
After the WP10--13 campaign (recorded in the program repository):
E2 is \emph{discharged} (the Family-B count holds unconditionally via
witness truncation); the sum-branch gap G1 is \emph{closed} (verified);
E1 is proved modulo classical inputs along the lattice route, with the
remaining write-up folded into the chain documents. The two genuinely
open estimates --- the lower-bound forms of E3 and C$^\dagger$ --- have
been reduced, through an eight-formulation ladder with unconditional
floor theorems at every elementary level, to \textbf{one exactly-stated
sign-sensitive divisor-correlation estimate} (two equivalent forms; the
same genus appears in both bricks). The estimate, its truth evidence,
its complete obstruction map, and the precise payoff are stated
self-containedly in the companion document
\texttt{THE-OPEN-PROBLEM.md}; the audited external-literature
dependencies of the conditional theorem are tabulated in
\texttt{literature-dependencies.md}.

\subsection*{Citation debts (classical, sourced, non-structural)}
\begin{itemize}
\item[(SL1)] Exponential sums over primes with hyperbolic phases
(Lemma~\ref{lem:SL1}; Vaughan + van der Corput, \cite[Ch.~13]{IK04}).
Feeds the partial E1 results (\S\ref{sec:e1e2}).
\item[(SL2/SL2$'$)] Linear rational phases over primes / the
$\psi$-over-primes cancellation (Lemmas~\ref{lem:SL2},~\ref{lem:SW};
Vinogradov). Feed E2 and Siegel--Walfisz for $g_{\mathbf z}$.
\item[(DMV)] The quantitative Daboussi--Montgomery--Vaughan bound
(Lemma~\ref{lem:DMV}), uniform over $1$-bounded multiplicative
weights. Feeds the weighted minor pairs of Lemma~C.
\item[(Hal)] A Hal\'asz--MRT-type mean-value input for the
major-pair absorption (remark after
Proposition~\ref{prop:C-weighted}).
\item[(TT)] \cite{TT25}, Theorem~3.1 --- statement verified against
the v2 source; transcription into the final manuscript pending.
\item[(GS/DGS)] \cite{GS} and the smooth-supported extension
(Drappeau--Granville--Shao) at the stated ranges.
\item[(Vin)] (Absorbed into Hypothesis E3: the extreme anatomy range
is beyond-$\sqrt{}$, not classical.)
\end{itemize}

\subsection*{Mechanical write-ups}
\begin{itemize}
\item[(W1)] Uniformity bookkeeping in $(q,\mu,p)$ across the digit
layer's minor/major assembly (\S\ref{sec:major}).
\item[(W2)] The fine-class inclusion--exclusion bookkeeping
(\S\ref{sec:anatomy}, item (iii); structure verified, WP2.4).
\item[(W3)] The FK gluing for Lemma C: carrying the weight through
\cite{FK21} \S\S3--5 with Propositions~\ref{prop:C-cov}--%
\ref{prop:C-single} as inputs.
\item[(W4)] The Dickman--Billingsley identification of the band sums
$\Sigma_{\mathbf j}$ with the box measures
(Proposition~\ref{prop:B-assembled}).
\item[(W6/W6$'$)] Generalized interpolation (bounded multiplicity, general bands) and the scale-drift average conversion for Lemma B (\S\ref{sec:lemmaB-closure}).
\item[(W5)] Final manuscript assembly: theorem statements
re-verified against the composed error budget of
Proposition~\ref{prop:cascade}.
\end{itemize}

\subsection*{Status summary}
\begin{center}
\begin{tabular}{ll}
\toprule
Piece & Status after verification (June 10, late)\\
\midrule
Lemma 0, margins (0$'$) & \statusP{} (Chernoff-repaired,
\S\ref{sec:bookkeeping})\\
Lemma A & \statusP{} (repaired, \S\ref{sec:bookkeeping})\\
Lemma B & \statusP{} modulo (TT), (SL2$'$), (W4), (W6$'$)\\
Lemma C, unweighted core & reduced to \S\S\ref{sec:minor}--\ref{sec:major}
(Prop.~\ref{prop:C-cov})\\
Lemma C, weighted layer & \statusO{} modulo C$^\dagger$\\
D$^\dagger$: deep harmonics & \statusP\\
D$^\dagger$: digit, minor & \statusP{} (verified; constants repaired)\\
D$^\dagger$: digit, major & \statusO{} modulo E1, E2 (partial E2;
routes named)\\
D$^\dagger$: anatomy & \statusO{} modulo E3\\
Depth packaging (D5) & \statusP{} (\S\ref{sec:bookkeeping})\\
Assembly cascade & \statusP{} given A--D (rate unspecified)\\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Trims (lower-bound track unaffected)}
Top of band $u,u'\le\tfrac12-\eta$; corner
$\sqrt R\ge\Llog^{B/2+c+5}$; slot-boundary slivers $O(\varepsilon')$;
margin costs (now proved free). For Theorem~\ref{thm:lower}: E1/E2 are
not needed (worst-case-per-modulus versions suffice), and a single
positive-proportion anatomy class suffices.

\subsection*{Known dead ends (recorded; do not re-enter)}
Union bounds across the digit layer (failure mass $\Theta(1)$);
smooth-cofactor designs ($\rho(c/\delta)$ loses to $e^{-c/\delta}$);
absolute-counting comparisons at any smoothness level (WP5 \S3:
requires $u<2^{1/(k+1)}$ against the forced $u\ge2$);
the semiprime trick; TT/Pilatte as a black box (dilation);
crude Cauchy--Schwarz over the mod-$q$ family;
Heilbronn completion via max-over-intervals;
the citation-adaptation route $\alpha+\beta$
(Remark~\ref{rem:negative}); single-scale (M2) and the polylog minor
claim (Remark~\ref{rem:M2-strengthening}); pure Balog--Wooley plus
CRT forcing (entropy count, WP5 \S5).
