\section{Appendix: numerical verification record}\label{app:numerics}

All scripts live in the program repository; this appendix records what
was verified and at what scale. Machine verification is treated as
evidence about \emph{truth}, never as proof; statements verified here
but not proved carry their own status tags in the text.

\subsection*{Lemma 0 (\texttt{lemma0\_test.py})}
Both sandwich inclusions: zero exceptions on $3\le n\le6\times10^4$.
$|D_0^{(+)}|=|D_0|$ exactly on this range; $|D_0^{(-)}|$ is $2\%$
larger; the lower set captures $98.7\%$ of $\W$. Margin symmetric
difference measured $\approx6\times10^{-5}$ at $10^9$. Measured pair
density at $10^9$: $0.92\,c_1^2$ (finite-scale, converging, drift
direction matching FK's own slow convergence).

\subsection*{Deep large sieve (\texttt{verify\_dls.py})}
The homomorphism identities \eqref{eq:fq-hom}, Wieferich orthogonality,
and the linearization of Lemma~\ref{lem:linearization}: exact (randomized,
$q\le1009$, and re-run June 9, 2026 on the program machine: all PASS).
Energy bound of Proposition~\ref{prop:energy}: ratio
$E/(N^2/q+qN)\le0.75$ across $q\in\{101,401,1009\}$, $N\le3q^2$,
approaching $1$ at $N\asymp q^2$ as the proof predicts. Observed RMS of
$|S(\lambda)|$ over initial segments far below the proven $\sqrt{qN}$
(e.g.\ $q=1009$, $N=255272$: observed $356$ vs guaranteed $16049$ vs
trivial $255272$).

\subsection*{Band empirics at $x=10^8$ (\texttt{empirics\_d.py})}
The exact D$^\dagger$ integrand $T_q(\lambda)$ on real coupled
populations (one simple band prime, cofactor digit decoration), five
strata $\gamma\in\{0.37,0.40,0.43,0.46,0.48\}$, populations
$3.6$k--$27.5$k:
\begin{center}
\begin{tabular}{cccccc}
\toprule
$\gamma$ & $q$ & $N_{\mathrm{pop}}$ & RMS $z$ & max $z$ &
unweighted control $z$ ($\lambda=1,2,3$)\\
\midrule
0.37 & 919  & 27531 & 0.95 & 1.77 & 0.88, 0.45, 0.77\\
0.40 & 1597 & 15854 & 1.19 & 2.53 & 0.52, 0.16, 0.87\\
0.43 & 2767 & 9161  & 1.22 & 2.20 & 2.27, 1.25, 0.74\\
0.46 & 4787 & 5273  & 1.19 & 2.01 & \textbf{5.47}, 1.93, 1.53\\
0.48 & 6947 & 3615  & 1.39 & 2.46 & \textbf{3.72, 3.23, 2.97}\\
\bottomrule
\end{tabular}
\end{center}
($z=|T|/\sqrt{\sum w^2}$; square-root cancellation $\Rightarrow z=O(1)$;
correlation-scale signal would be $z\approx30$--$80$.) Decorated sums
flat at every stratum even where the unweighted control blows up
(top strata): empirical confirmation of the division of labor between
Lemmas B/C (population shape) and D (decoration decorrelation). The
small-$\lambda$ drift at top of band ($z$: $0.82\to2.46$) is the
$\mu/\lambda=1$ major arc announcing itself
(Definition~\ref{def:dichotomy}); interior-$p$ restriction flattens it.

\subsection*{Two-frequency reduction at $x_{\mathrm{model}}=10^{11}$
(\texttt{wp21\_test.py})}
$q=4787$, $\lambda\in\{1,2\}$, 260 primes $p\in[3000,60000]$,
$\sigma\equiv1$: linearized phase equals the true Fermat-quotient phase
to $10^{-14}$; median $z=|V|/\sqrt{R/4}=0.08$, 90th percentile $0.40$,
aggregate $\sum_p|V_p|=0.8\%$ of trivial; major arcs observed exactly on
the predicted curves ($p=4759,4813\approx q$: the $\mu/\lambda=1$ curve,
$|V|\approx0.3R$, $z\approx41$; $p=8171$ at $\lambda=2$:
$(p/q)^2\approx2.91$, the $\mu/\lambda=3$ curve). All 26 cases exceeding
a naively truncated bound trace to major-arc width undercounting, none
to a failure of the mechanism.

\subsection*{Anatomy unwinding (WP2.3 session checks)}
The identity of Proposition~\ref{prop:one-large}: zero violations on the
actual progressions; the decomposition of
Proposition~\ref{prop:species}: exact to $10^{-14}$; friable-weighted
minor-frequency sums at $z=O(1)$.

\subsection*{E1/E2 diagnosis probes (\texttt{e1\_probe.py},
\texttt{e2\_probe.py}; June 9, late)}
E1 at model scale $10^{11}$ ($\Llog^B=50$, $\mu\le30$,
$\lambda\in\{1,2\}$, 60 moduli per geometry): signed
$\mathrm{avg}_q\sum_\mu E_q\in\{-3.5,\ldots,+0.6\}$ against main terms
$15$--$155$ and worst-case bounds $282$--$5065$ --- the signed average
(Remark~\ref{rem:E1-signed}) is $1$--$4\%$ of the main term in both
geometries. E2: the tail law
$\Pr[\text{max gap ratio}>G]\cdot G\approx5$--$9$ holds for
$G=10\ldots1000$ in both geometries; $\mathbb E[\mathcal D_R]\approx14$,
$\mathbb E[\mathcal D_R^2]\approx210$ (polylog, as
Proposition~\ref{prop:familyB} asserts); the structural first gap
appears at median ratio $3.0\sim p/q$ in the $u>u'$ geometry and is
absent ($2.0$, generic) in $u<u'$ --- exactly the corrected picture of
Remark~\ref{rem:M2-strengthening}.

\subsection*{Fine-anatomy-class probe (\texttt{fine\_class\_probe.py};
ledger item D4)}
Class-restricted populations at $x=10^8$, $\gamma\in\{0.40,0.43\}$:
bare friable (N $=13709/7948$), $P^+(a)\in(x^{0.20},x^{0.28}]$
($5904/3436$), $P^+(a)\le x^{0.20}$ ($2933/1700$): decorated RMS $z$
between $1.00$ and $1.66$ in every class at every stratum
(correlation scale would be $z\approx30+$): the digit decoration
decorrelates within every fine class, as the conditional architecture
requires.
