\begin{thebibliography}{99}
\itemsep2pt

\bibitem{BZ08} S.~Baier and L.~Zhao,
\emph{An improvement for the large sieve for square moduli},
J. Number Theory \textbf{128} (2008), 154--174.

\bibitem{dlBG22} R.~de la Bret\`eche and A.~Granville,
\emph{Exponential sums with multiplicative coefficients and applications},
Trans. Amer. Math. Soc. \textbf{375} (2022).

\bibitem{dlBT07} R.~de la Bret\`eche and G.~Tenenbaum,
\emph{Sommes d'exponentielles friables d'arguments rationnels},
Funct. Approx. Comment. Math. \textbf{37} (2007), 31--38.

\bibitem{DGS17} S.~Drappeau, A.~Granville and X.~Shao,
\emph{Smooth-supported multiplicative functions in arithmetic
progressions beyond the $x^{1/2}$-barrier}, Mathematika \textbf{63}
(2017); arXiv:1704.04831. (Located; statement used at abstract grade
--- the weakest load-bearing item per \texttt{literature-dependencies.md}.)

\bibitem{Drap15} S.~Drappeau,
\emph{Th\'eor\`emes de type Fouvry--Iwaniec pour les entiers friables},
Canad. J. Math. \textbf{67} (2015), 597--638.

\bibitem{DS16} S.~Drappeau and X.~Shao,
\emph{Weyl sums, mean value estimates, and Waring's problem with friable
numbers}, Acta Arith. \textbf{176} (2016), 249--299.

\bibitem{ErGr80} P.~Erd\H{o}s and R.~L. Graham,
\emph{Old and new problems and results in combinatorial number theory},
Monographies de L'Enseignement Math\'ematique \textbf{28}, Gen\`eve, 1980.
(Erd\H{o}s problem 396.)

\bibitem{FK21} K.~Ford and S.~Konyagin,
\emph{Divisibility of the central binomial coefficient $\binom{2n}{n}$},
Trans. Amer. Math. Soc. \textbf{374} (2021), 923--953;
arXiv:1909.03903.

\bibitem{FT91} \'E.~Fouvry and G.~Tenenbaum,
\emph{Entiers sans grand facteur premier en progressions arithm\'etiques},
Proc. London Math. Soc. \textbf{63} (1991), 449--494.

\bibitem{Gar06} M.~Z. Garaev,
\emph{On multiplicative congruences},
Monatsh. Math. \textbf{148} (2006). (The completion method underlying
\cite{Shp11}, Theorem 8.)

\bibitem{GS} A.~Granville and X.~Shao,
\emph{Bombieri--Vinogradov for multiplicative functions, and beyond the
$x^{1/2}$-barrier}, Adv. Math. \textbf{350} (2019), 304--358.

\bibitem{Harper16} A.~J. Harper,
\emph{Minor arcs, mean values, and restriction theory for exponential
sums over smooth numbers}, Compos. Math. \textbf{152} (2016), 1121--1158.

\bibitem{HB96} D.~R. Heath-Brown,
\emph{An estimate for Heilbronn's exponential sum},
in: Analytic Number Theory: Proceedings in honor of H.~Halberstam,
Birkh\"auser, 1996, 451--463.

\bibitem{HBK00} D.~R. Heath-Brown and S.~Konyagin,
\emph{New bounds for Gauss sums derived from $k$th powers, and for
Heilbronn's exponential sum}, Q. J. Math. \textbf{51} (2000), 221--235.

\bibitem{Hil85} A.~Hildebrand,
\emph{On a conjecture of Balog}, Proc. Amer. Math. Soc. \textbf{95}
(1985), 517--523.

\bibitem{IK04} H.~Iwaniec and E.~Kowalski,
\emph{Analytic Number Theory}, AMS Colloquium Publications \textbf{53},
2004.

\bibitem{Khin} A.~Ya. Khinchin, \emph{Continued Fractions},
University of Chicago Press, 1964.

\bibitem{MRT} K.~Matom\"aki, M.~Radziwi\l\l{} and T.~Tao,
\emph{An averaged form of Chowla's conjecture},
Algebra Number Theory \textbf{9} (2015), 2167--2196.
(With its successors: multiplicative functions in short intervals;
averaged Elliott.)

\bibitem{Pil23} C.~Pilatte,
\emph{Improved bounds for the two-point logarithmic Chowla conjecture},
arXiv:2310.19357.

\bibitem{Pom15} C.~Pomerance,
\emph{Divisors of the middle binomial coefficient},
Amer. Math. Monthly \textbf{122} (2015), 636--644.

\bibitem{Shp11} I.~E. Shparlinski,
\emph{Character sums with Fermat quotients},
Bull. Lond. Math. Soc. \textbf{43} (2011);
arXiv:1104.3909. (Theorem 8 and the remark (10) on arbitrary primitive
characters mod $p^2$; close-read against the source June 9, 2026.)

\bibitem{TT25} T.~Tao and J.~Ter\"av\"ainen,
\emph{Quantitative correlations and some problems on prime factors of
consecutive integers}, arXiv:2512.01739 (December 2025).
(Theorem 3.1 verification pending: items B1--B3 of
\S\ref{sec:remaining}.)

\bibitem{Ter18} J.~Ter\"av\"ainen,
\emph{On binary correlations of multiplicative functions},
Forum Math. Sigma \textbf{6} (2018), e10; arXiv:1710.01195.

\bibitem{Vau97} R.~C. Vaughan,
\emph{The Hardy--Littlewood Method}, 2nd ed., Cambridge Tracts in
Math. \textbf{125}, Cambridge University Press, 1997. (Lemma 2.2-type
inhomogeneous Vinogradov counting.)

\end{thebibliography}
